Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-05 article.tex
Pretty Markov chain
Markov chain has a good caption

\input{markov_chain.latex}

>>>>

\begin{figure}
  \centering
  \input{markov_chain.latex}
  \caption{
    State transitions in TMHs caused by mutations, with respect to the
    detection by the immune system. Any TMH is either in a detected, $D$, or
    undetected, $U$, state. Mutations cause state transitions with probability
    $p$. For example, $p_{DU}$ denotes the probability that a detected
    TMH mutations into an undetected one.
  }
  \label{fig:markov_chain}
\end{figure}
